The Heavy Photon Search Test Detector

### 2013-11-06 hps-testrun-nim.tex
Moved performance from SVT and ECal to its own section

\subsection{Monitoring and Calibration}

\subsection{Data Analysis and Performance}

\subsubsection{Alignment}
The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
optical survey of individual modules with precision of a few $\mu$m are combined with a touch-prove survey 
of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
respect to the support plates and the mechanical survey balls on the base plate.
After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate position 
inside the pair spectrometer vacuum chamber is used to determine the global position of the SVT with 
respect to CEBAF beam line. 
The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
microns. A more sophisticated global track-based alignment technique to reach the final alignment precision 
is being developed.

@@

\subsection{Calibration and Performance}
\label{sec:ecal_calibration}

@@

\subsection{Performance}
As discussed above, the trigger and DAQ integrate pulses differently to measure hit energy. The trigger 
integrates using a time-over-threshold window, and the DAQ readout integrates using a constant window 
(5 samples before and 30 samples after a threshold crossing). For every event, the trigger reports the 
trigger decision as a bit mask (top trigger, bottom trigger, or both) and the time the trigger fires.

>>>>

\subsection{Alignment}
The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
optical survey of individual modules with precision of a few $\mu$m are combined with a touch-prove survey 
of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
respect to the support plates and the mechanical survey balls on the base plate.
After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate position 
inside the pair spectrometer vacuum chamber is used to determine the global position of the SVT with 
respect to CEBAF beam line. 
The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
microns. A more sophisticated global track-based alignment technique to reach the final alignment precision 
is being developed.

@@

@@

\section{Performance}

\subsection{SVT Performance}

\subsection{ECal and Trigger Performance}
\label{sec:ecal_calibration}

%\subsubsection{ECal Calibration and Performance}

%\subsubsection{Trigger Performance}
As discussed above, the trigger and DAQ integrate pulses differently to measure hit energy. The trigger 
integrates using a time-over-threshold window, and the DAQ readout integrates using a constant window 
(5 samples before and 30 samples after a threshold crossing). For every event, the trigger reports the 
trigger decision as a bit mask (top trigger, bottom trigger, or both) and the time the trigger fires.
